Study of the Empirical Distribution of Ties in Irrational Numbers

### 2020-11-14 Reports/Report - Data Imputation/Code/EmpiricalDistributionTies.Rmd
Monte Carlo

---
title: "Study of the Empirical Distribution of Ties in Irrational Numbers"
author: "Eduarda Chagas"
date: "Nov 10, 2020"

output: html_notebook
---

@@

>>>>

---
title: "Study of the Empirical Distribution of Ties in Irrational Numbers"
author: "Eduarda Chagas"
date: "Nov 10, 2020"
output:
  html_document:
    df_print: paged
---

@@

# Monte Carlo study

The purpose of the study is measuring the ability of imputation methods (list here which ones we will consider: I suggest the two best ones reported in the literature) to retrieve the underlying dynamic of a time series that has been *attacked*.
In a loose sense, we will assess the *breakdown point* of the imputation techniques (study references for "breakdown poiont").
The **attack** consists in introducing randomly repeated values in the sequence.

```{r PSEUDOCODE eval=FALSE}
# Define imputation techniques as functions
I1 <- function(time_series, params=...){return(imputed_time_series)}
I2 <- function(time_series){return(imputed_time_series)}

# Define attack
# Input:  "time_series" a time series without repetitions
#         "d" embedding dimension
#         "p" probability of attack
AttackTimeSeries <- function(time_series, d, p) {
  attacked_time_series <- time_series
  foreach(d in time_series) { # Check the package foreach
    if (runif(1) <= p) { # attack with probability p
      select uniformly an observation in d, say at position i
      select uniformly a position in d different from i, say j
      replace d[j] <- d[i] # this introduces a repetition
    }
  }
  return(attacked_time_series)
}

# Define the parameter space of the Monte Carlo study
# My suggestion: white noise, for which we already have confidence intervals in the HxC plane

N <- c(N1, N2, N3, ...) # lengths of the time series to be considered
D <- c(D1, D2, D3, ...) # embedding dimensions to be considered
P <- c(p1, p2, p3, ...) # probabilities of attack to be considered

# Store all the points in the HxC plane of the following loop
for(n in N){
  for(d in D) {
    for(p in P) {

      x <- white_noise_length_n # perhaps from the true noise we already have
      hcx <- point_in_the_HC_plane(x)
      x_attack <- AttackTimeSeries(x, d, p)
      hcxattack <- point_in_the_HC_plane(x_attack)

    }
  }
}

# Analyze the points, for instance:
# Measure distances between pairs
# Count the number of points inside the confidence regions
```
